Tempo and mode of promoter evolution as observed in the \textit{Paramecium aurelia} species complex

### 2020-07-07 manuscript.tex
Added a bit to introduction.

Main et al. \citep{Main:2013dg}, used a separate TSS profiling method in \textit{D. melanogaster} to identify putative orthologous TSSs in three other \textit{Drosophila} taxa: \textit{D. simulans}, \textit{D. pseudoobscura} and \textit{D. sechellia}. The authors found that the location and estimated activities of orthologous TSSs to be generally conserved, but did observe instances of TSS variation that suggest new promoters. Notably, \textit{Main et. al.} found differences in promoter selection in the Alcohol dehydrogenase (ADH) gene across the four species. Working with high-resolution promoter data in human and mouse, Young and colleagues \citep{Young:2015xx} found that more than half (56\$) of tissue-matched promoters were turned over between the two species. Noting that most protein-coding genes in mammals \citep{FANTOMConsortiumandtheRIKENPMIandCLSTDGT:2014hz} have multiple promoters, the authors propose that promoter turnover is an important but overlooked means by which transcriptional modules diverge during evolution. Add bit about paralogs and how we can use them to help us understand how \textit{cis}-regulatory regions evolve. -> we haven't studied the fate of cis-regulatory regions in ortho-paralog pairs. then:

>>>>

Main et al. \citep{Main:2013dg}, used a separate TSS profiling method in \textit{D. melanogaster} to identify putative orthologous TSSs in three other \textit{Drosophila} taxa: \textit{D. simulans}, \textit{D. pseudoobscura} and \textit{D. sechellia}. The authors found that the location and estimated activities of orthologous TSSs to be generally conserved, but did observe instances of TSS variation that suggest new promoters. Notably, \textit{Main et. al.} found differences in promoter selection in the Alcohol dehydrogenase (ADH) gene across the four species. Working with high-resolution promoter data in human and mouse, Young and colleagues \citep{Young:2015xx} found that more than half (56\$) of tissue-matched promoters were turned over between the two species. Noting that most protein-coding genes in mammals \citep{FANTOMConsortiumandtheRIKENPMIandCLSTDGT:2014hz} have multiple promoters, the authors propose that promoter turnover is an important but overlooked means by which transcriptional modules diverge during evolution. Interestingly, while the fates of ortho-paralog pairs that arise through whole genome duplication (WGD) has been heavily studied (enter citations for Ohno, 1970; Wolfe and Shields, 1997, Force et al., 1999, others), the behavior of \textit{cis}-regulatory regions of duplicate gene pairs is less well-understood. (Add a bit about paralogs and how we can use them to help us understand how \textit{cis}-regulatory regions evolve. -> we haven't studied the fate of cis-regulatory regions in ortho-paralog pairs.) then:
